{Automatic Least-Effort Contextual Learning}

### 2017-02-27 etc/paper.tex
[paper] mention Marr-Poggio levels and WWW/Internet analogy

The goals of SKN are to augment learning mechanisms around \emph{contextual}
knowledge in a manner that reduces the intractability of hard problems by
implicitly relating knowledge in a non-flat structure, enabling
compositionality at arbitrary scale.

@@

>>>>

The goal of SKN is to augment learning mechanisms around \emph{contextual}
knowledge in a manner that reduces the intractability of hard problems by
implicitly relating knowledge in a non-flat structure, enabling
compositionality at arbitrary scale. In terms of the Marr-Poggio levels of
analysis \cite{marr78}, SKN serves as a tool on the algorithmic level of
abstraction, not as a description of hardware-level structure --- analogous
to the World Wide Web operating at a higher level over the Internet.

@@

  \bibitem{marr78}
    Marr, D., \& Poggio, T. (1976).
    From understanding computation to understanding neural circuitry.
